Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-16 Scripts/Initial_Analysis.Rmd
Changes to make it run on Hall

dbem_import(
#   taxon_key <- 600004,
#   iyr <- 1951,
#   fyr <- 1952,
#   data_type <- "Abd",
#   ensamble_list = c(102,103),
#   Path <- DBEM_path
# )

@@

iyr <- 1951
fyr <- 1953
data_type <- "Catch"
ensamble_list = seq(102,103,1)
DBEM_path <- "/Volumes/DATA/DATA/DBEM/"
world_grid <- tibble(index = seq(1,259200,1))
Neighbours <- read_excel(paste(data_path,"Spatial/EEZ_Neighbour_List.xlsx",sep="")) %>% 
  clean_names()

@@

Spp_list <- unique(Transboundary_spp$taxon_key)

@@

suppressWarnings(
  r_proportion_change <- bind_rows(
    lapply(
      Spp_list[1:2], #c(600004,600005),
      EstPropChange,
      iyr <- iyr,
      fyr <- fyr,
      data_type <- "Catch",
      ensamble_list = ensamble_list,
      Path =DBEM_path,
      Neighbours = Neighbours
    )
  )
)

>>>>

# dbem_import(
#   taxon_key <- 600004,
#   iyr <- 1951,
#   fyr <- 1952,
#   data_type <- "Abd",
#   ensamble_list = c(102,103),
#   Path <- DBEM_path
# )

@@

iyr <- 1951
fyr <- 2099
data_type <- "Catch"
ensamble_list <- seq(102,111,1)
DBEM_path <- "/Volumes/DATA/DATA/DBEM/"
world_grid <- tibble(index = seq(1,259200,1))
Neighbours <- read_excel(paste(data_path,"Spatial/EEZ_Neighbour_List.xlsx",sep="")) %>% 
  clean_names()

@@

Spp_list <- unique(Transboundary_spp$taxon_key)[3:4]

@@

# suppressWarnings(
  r_proportion_change <- bind_rows(
    lapply(
      Spp_list, #c(600004,600005),
      EstPropChange,
      iyr <- iyr,
      fyr <- fyr,
      data_type <- "Catch",
      ensamble_list = ensamble_list,
      Path =DBEM_path,
      Neighbours = Neighbours
    )
  )
# )

write_csv(r_proportion_change,
          "r_proportion_change.csv")
